\documentclass[sigconf]{acmart}

\input{format/i523}

\begin{document}
\title{Using Big Data to Battle Air Pollution}

\author{Karthik Vegi}
\affiliation{%
  \institution{Indiana University Bloomington}
  \streetaddress{2619 East 2nd Street, Apt 11}
  \city{Bloomington, IN 47401} 
  \country{USA}}
\email{kvegi@iu.com}


% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{kvegi}


\begin{abstract}
We have come a long way from the stone age to build large scale industries, big cities, bullet trains, and a booming automobile industry. Technological and industrial advances are making our cities smarter by the day and yet a nagging side-effect is air pollution. Air pollution is not only creating local health hazards like respiratory and heart problems, but also directly leading to an increase in temperatures and contributing to global warming. We show how the advances in {\em Big Data}, {\em Cloud Computing}, and {\em Internet Of Devices} can be used to combat air pollution.
\end{abstract}

\keywords{i523, hid231, big data, environment, air pollution, global warming}

\maketitle

\section{Introduction}

{\em Big Data} is playing a crucial role in building a smarter planet. Each and every action that we take leaves a digital footprint. Big Data is lending a great helping hand to crunch this data and make smarter decisions. ``{\em Big Data} is at the heart of the smart revolution. It is already completely transforming the way we live, find love, cure cancer, conduct science, improve performance, run cities, and countries and operate business'' \cite{Marr2015}.  

\bibliographystyle{ACM-Reference-Format}
\bibliography{report} 

\end{document}
